---
output: github_document
---

[![Build status](https://ci.appveyor.com/api/projects/status/fju06tfixss6dce8?svg=true)](https://ci.appveyor.com/project/masalmon/eml-tools)
[![Build Status](https://travis-ci.org/maelle/eml.tools.svg?branch=master)](https://travis-ci.org/maelle/eml.tools)
[![codecov](https://codecov.io/gh/maelle/eml.tools/branch/master/graph/badge.svg)](https://codecov.io/gh/maelle/eml.tools)

Package in construction for using EML (Ecological Metadata Language) in data analysis, currently only one function. For creating a new EML, see the [rOpenSci `EML` package](https://github.com/ropensci/EML).

# Translating factors into their meanings

# When the EML only has one table

```{r}
library("eml.tools")
data("animals_eml")
data("animals_data")
animals_data
eml_translate_factors(df = animals_data, eml = animals_eml, keep = FALSE)
eml_translate_factors(df = animals_data, eml = animals_eml, keep = TRUE)

```


# When the EML only has several tables

This is the case if the EML documents a database. In this case, we need to use the entityName of the table for which we want to perform the translation.

```{r}
library("eml.tools")
data("animals_db_eml")
data("animals_data")
animals_data
eml_translate_factors(df = animals_data,
                      eml = animals_db_eml,
                      which_table = "english_animals",
                      keep = FALSE)
eml_translate_factors(df = animals_data,
                      eml = animals_db_eml,
                      which_table = "english_animals",
                      keep = TRUE)

```
